Journey: A Study of Scalabilty of Memory Management in Linux (TODO: should we get a new title?)

### 2017-04-28 paper.tex
Added figure positions and worked on conclusions

\begin{figure}
\centering
\begin{tabular}{|l|p{5cm}|} \hline
OS & Ubuntu 16.04.2 \\ \hline
Kernel & Linux 4.4.0-70 \\ \hline
CPU & Intel Xeon E5645, 2.40 GHz, 6 cores/12 threads, 32kB L1-D, 32kB L1-I,
    256kB L2, 12MB L3 \\ \hline
Memory & 16GB, 1066MHz \\ \hline
Storage & 500GB HDD, 7200RPM \\
\hline
\end{tabular}
\caption{Specifications of our test machine.  \label{fig:specs}}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/mmap_latency}
    \caption{Latency of memory operations}
    \label{fig:mmap_latency}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/mmap_mem_usage}
    \caption{$\Delta_i$ adjusted with control for benchmarks}
    \label{fig:mmap_mem_usage}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/vm_area_struct_count}
    \caption{Number of \texttt{vm\_area\_struct}s for benchmarks}
    \label{fig:vm_area_struct_count}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_rss}
    \caption{RSS while touching pages while swapping for random benchmark.}
    \label{swap_rss}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_cont_cdf}
    \caption{CDF of time to touch a page while swapping for continuous
    benchmark. Notice that the y-axis scale is from 99.75\% to 100\%.
    \label{fig:swap_time_cont_cdf}}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_rand_cdf}
    \caption{CDF of time to touch a page while swapping for random benchmark.
    Notice that the y-axis scale is from 93\% to 100\%.\label{fig:swap_time_rand_cdf}}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_time_cont}
    \caption{Time to touch a page while swapping for continuous benchmark.
    Notice that the y-scale is logarithmic.\label{fig:swap_time_cont}}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_time_rand}
    \caption{Time to touch a page while swapping for random
    benchmark.\label{fig:swap_time_rand}}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_time_cdf}
    \caption{CDF of amount of time spent on operations with a given
    latency.\label{fig:swap_time_cdf}}
\end{figure}

@@

Large swap files should be created with disk locality or on SSDs.

Looking at 99.99-th percentile latencies is important because they can have a
large impact on overall run time.

TODO: what else?

TODO: time: MARKM

TODO: khugepaged?

>>>>

\begin{figure}[t]
\centering
\begin{tabular}{|l|p{5cm}|} \hline
OS & Ubuntu 16.04.2 \\ \hline
Kernel & Linux 4.4.0-70 \\ \hline
CPU & Intel Xeon E5645, 2.40 GHz, 6 cores/12 threads, 32kB L1-D, 32kB L1-I,
    256kB L2, 12MB L3 \\ \hline
Memory & 16GB, 1066MHz \\ \hline
Storage & 500GB HDD, 7200RPM \\
\hline
\end{tabular}
\caption{Specifications of our test machine.  \label{fig:specs}}
\end{figure}

@@

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/mmap_latency}
    \caption{Latency of memory operations}
    \label{fig:mmap_latency}
\end{figure}

@@

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/mmap_mem_usage}
    \caption{$\Delta_i$ adjusted with control for benchmarks}
    \label{fig:mmap_mem_usage}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/vm_area_struct_count}
    \caption{Number of \texttt{vm\_area\_struct}s for benchmarks}
    \label{fig:vm_area_struct_count}
\end{figure}

@@

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/swap_rss}
    \caption{RSS while touching pages while swapping for random benchmark.}
    \label{swap_rss}
\end{figure}

@@

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_cont_cdf}
    \caption{CDF of time to touch a page while swapping for continuous
    benchmark. Notice that the y-axis scale is from 99.75\% to 100\%.
    \label{fig:swap_time_cont_cdf}}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_rand_cdf}
    \caption{CDF of time to touch a page while swapping for random benchmark.
    Notice that the y-axis scale is from 93\% to 100\%.\label{fig:swap_time_rand_cdf}}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/swap_time_cont}
    \caption{Time to touch a page while swapping for continuous benchmark.
    Notice that the y-scale is logarithmic.\label{fig:swap_time_cont}}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/swap_time_rand}
    \caption{Time to touch a page while swapping for random
    benchmark.\label{fig:swap_time_rand}}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/swap_time_cdf}
    \caption{CDF of amount of time spent on operations with a given
    latency.\label{fig:swap_time_cdf}}
\end{figure}

@@

While large swap files allow greater amount of memory overcommitment, they can
also reduce the degree of disk locality. Thus, large swap files should be
created with disk locality in mind or on SSDs. Some Linux distributions, such as
Ubuntu, have switched to using swap files rather than swap partitions by default
(TODO: cite). Our results suggest that for some workloads this may have a
negative impact on performance if the swapfile ends up in non-continuous disk
locations.

Also, looking at 99.99-th percentile latencies is important because they can
have a large impact on overall run time. As our results show, even very uncommon
high-latency operations may have a significant impact on performance.

\subsection{kswapd and khugepaged (TODO: markm)}

TODO

TODO
